---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foodSeq

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of foodSeq like so:

This chunk will be for future use when I can actually push to my github rip :(
``` {r install, eval = FALSE}
# # 1. Install bioconductor and devtools if needed
# # This package depends on Bioconductor packages (phyloseq, microbiome) 
# if (!requireNamespace("BiocManager", quietly = TRUE)){
#   install.packages("BiocManager")
# }
# 
# if (!requireNamespace("devtools", quietly = TRUE)) {
#   install.packages("devtools")
# }
# 
# library(devtools)
# library(BiocManager) 
# 
# # 2. Install the package
# devtools:install_github("cr403/foodSeq") 
# 
# # 3. Load library
# library(foodSeq)
```

For now, this is the workaround: 

Within the foodSeq project, run the following chunk. Now, you should be able to load this repo like a regular package in another project. 
```{r}
devtools::install_local() 
```

## Loading Updates
To check for updates, you can run this chunk within your desired project--**NOT within foodSeq project/repo**. This will uninstall and reinstall the package without the need for restarting your R session. It's commented out here so that the Rmd file will knit. 
```{r}
# detach("package:foodSeq", unload = TRUE)
# devtools::install("~/Library/CloudStorage/Box-Box/project_davidlab/LAD_LAB_Personnel/Caroline_R/10_Repo/foodSeq")
# library(foodSeq)
```

